\section{Discussion and conclusions}
\label{sec:discussion}
We have four topics to discuss here:
\begin{itemize}
\item \textbf{Velocity map binning methods:} a technical discussion on the comparative merits of alternative MaNGA velocity map binning methods and IFU sizes to obtain best resolution Radon profile traces.
\item \textbf{Correlation between Radon profiles classes and morphology:} we discuss a possible relationship between Radon transform trace profile Types and galaxy morphology.
\item \textbf{Findings and conclusions:} a review of the significant findings of the project and presentation of our conclusions.
\item \textbf{Future work:} some topics for future work noted during the course of the project. 
\end{itemize}

\input{sections/binning-methods.tex}

\subsection[Correlation between Radon profiles and morphology]{Correlation between Radon profile types and morphological features}
\label{sec:correlations}
\cite{2018MNRAS.480.2217S} made considerable efforts to explore  possible correlations between the observed frequencies of the 5 Radon profile types (Type-C, Type-A, Type-IB, Type-OB and Type-OB+IB) and underlying morphological features obtained from the Galaxy Zoo morphology classification project. They found some evidence of associations between Radon profile trace type and morphological features, as discussed in detail in their paper, Section 5. These correlations are subjective, however, and certainly not exclusive of other possible interpretations of Radon type to morphology relationships. We stress that Care must be taken to follow their arguments closely. In our opinion, the most assertive of those relationships can be broadly summarised as follows:
\begin{itemize}
\item Type-C: Constant profile - apparent in unbarred galaxies.
\item Type-A: Asymmetric profile - often associated with tidal interactions.
\item Type-IB: Inner bends - prevalent in strongly barred galaxies.
\item Type-OB: Outer bends - often associated with kinematic warps.
\end{itemize}

Following the above interpretation there are two relevant points to to the discussion. Firstly that Radon profile Type-OB outer bend features have an association with kinematic warps. In this way Type-OB profiles could represent the signatures of past mergers in disc galaxies. Secondly, if Radon Type-A asymmetric profiles are associated with tidal interactions and tidal tails, then Type-A profiles may represent the signatures of gas-poor, dry mergers in early-type galaxies, see e.g.  \cite{2005AJ....130.2647V}. 

%%%% ====================================

%%% Stopping here for the night ...

%%% =====================================

As reported in our results Section \ref{sec:comparison-of-results} we found that 5 out of 14 PSBs with large $\Delta$PA$_{k}$ offsets were assigned Radon profile trace classification of Type-OB. We emphasise that this result was determined by Classifier A, and there was little consensus with the classifications of either Classifier B, or in the limited number of automatic classifications that were available for our galaxies. Setting this point aside for now, some correlation may exist between Radon outer bend profiles, large $\Delta$PA$_{k}$ and past major mergers. Again we stress that much further work is required to provide consistent interpretations of Radon profile trace types before we can make this conclusion.

\subsection{Findings and conclusions}
\label{findings}

In our analysis of kinematic position angle offsets we have shown that CPSBs possess a wide range of $\Delta$PA$_{k}$ above 30\textdegree\ with many greater than 90\textdegree. RPSBs have a smaller range in $\Delta$PA$_{k}$, with only a few over 90\textdegree. The majority of control galaxies have small kinematic position angle differences, clustered at less than 25\textdegree. Significant misalignment in the gas and stellar velocity fields of CPSBs, and to a lesser extent in RPSBs, reveal kinematic disturbances indicative of past major mergers.
We noted that the distribution in $\Delta$PA$_{k}$ is markedly different when comparing CPSBs with the CPSB control set, and this trait is present, but to a lesser degree in the comparison of the RPSB $\Delta$PA$_{k}$ with their controls. The distribution in  kinematic position angle offsets is similar for both control sets. These observations are strongly supported by the results of K-S analysis in Section \ref{sec:K-S-test} where we found the difference in $\Delta$PA$_{k}$ of both PSB groups, as compared to their control groups, to be statistically significant. In summary, the most significant finding arising from the kinematic position analysis study is that there is a combination of mutually supportive evidence of past disruption derived from the properties of PSBs, and we can concluded that mergers play a role in galaxy evolution. This evidence was identified in three topics: the $\Delta$PA$_{k}$ distributions in the CPSB, RPSB and their control sets; the supporting K-S statistical analysis performed on these $\Delta$PA$_{k}$ distributions; and the differences in distributions of S\'ersic index. Taken together these indicators point towards an evolutionary sequence from normal, non-PSB (control) galaxies, to the lower S\'ersic index disc-like RPSBs, and on to the redder spheroidal CPSBs with higher S\'ersic indices. We see PSBs as the indicators of morphological transition from late-type disc galaxies to red spheroids depicting an evolutionary pathway from the blue cloud, through the green valley, towards the red sequence.

Before we present the main results of the Radon transform method, we summarise the technical discussion comparing the relative merits of MaNGA map binning schema and IFU size. We compared the Radon profile trace results obtained from stellar velocity maps employing Voronoi VOR10 binning versus the single spaxel SPX unbinned schema. We obtained cleaner trace profiles (i.e. easier to classify) with a greater number of valid data points and tighter error bars from high S/N maps based on single spaxel SPX binning. For future studies, given a large enough sample of PSBs, we should avoid Voronoi binned maps where possible and use SPX maps taking a cut of S/N greater than 3 or more in single spaxels.

A substantial effort was put into the visual classification of  Radon transform profile trace plots of the stellar velocity maps to determine their trace feature Types.  It was noted that visual classification was difficult. Our classifiers agreed on this point. In addition, our classifiers arrived at disparate, sometimes opposing interpretations of profile type class for most galaxies, even though the same written classification procedure was followed. We now recognise the difficulties in relating the trace plots to the 'standard' examples. With only two participating classifiers we conclude that there must be significant classification error present in our results, recalling that the Galaxy Zoo project engaged $\sim10^5$ classifiers to minimise classification error.

We compared the results of the kinematic PA analysis with those the Radon transform analysis technique. As mentioned in Section \ref{sec:motivation} the Radon transform method should provide distinct advantages over the kinematic $\Delta$PA$_{k}$ method. Radon transforms provide a detailed trace of position angle across the velocity field enabling local regions of radial variation to be identified. Kinematic PAs require both stellar and gas velocity fields to be mapped but post-starburst galaxies may possess little gas. The Radon transform can identify local regions of disturbance, as evidence of merger activity, using the stellar velocity field alone.

Earlier in this discussion (Section \ref{sec:correlations}) we put forward the notion that Radon profile Type-OB features may be consistent with kinematic warps in stellar discs, while Type-A profiles suggest the presence of tidal tails from interacting or merged early-type field galaxies. In both cases merged systems of sufficient age, 1 to 2 Gyr, will reveal the characteristics of post-starburst galaxies. We suggested that Radon trace profiles displaying outer bends, Type-OB or Type-OB+IB (indicating warped stellar discs) could be considered prospective candidates of past major mergers in disc-dominated systems, while Type-A profiles (consistent with tidal interactions) may correlate with ongoing or past mergers in elliptical systems. From Table \ref{tab:Radon-VC-results} we saw that Classifier A identified 10 of of 27 CPSBs (37\%), and 10 out of 36 RPSBs (28\%) as having Type-OB or Type-OB+IB Radon profile signatures. Type-A features were evident in  15\% of CPSBs and 19\% of RPSBs. If this classification is reliable, and the correlation between type and morphology is valid (there are considerable uncertainties in both these areas), then we could conclude that there is some evidence of past mergers in post-starburst galaxies. This tentative conclusion needs to be supported by further research into the areas of uncertainty: Radon profile classification and the correlation relationship between Radon type and morphology.

% \subsection{Summary}
% \label{summary}
In previous studies major mergers have been detected using imaging techniques. In this project we have attempted to identify past major mergers in PSB galaxies, firstly by investigating the distributions of differences in stellar and gas velocity field kinematic position angles, and secondly by using the Radon transform method to reveal radial variation in kinematic position angles. 
We obtained a positive result from the $\Delta$PA$_{k}$ analysis revealing that PSBs lie on a evolutionary track between the blue cloud and the red sequence. The Radon transform method, however, did not provide conclusive results. We attribute this to the difficulty in classifying kinematic features from the trace plots. More work is required to provide consistent classification of kinematic features apparent in the Radon profile trace plots. 

It was noted that \cite{2019DDA....5020304N} have recently announced work which promises to increase the accuracy of merger detection using a method that integrates imaging and kinematic analysis techniques. This extended method will combine SDSS imaging (providing morphological observations) with MaNGA  kinematic maps, towards enhanced identification of merger and post-merger signatures. When available, this technique should be applied to our PSB and control samples to provide additional evidence of past mergers in post-starburst galaxies.
